

%Section: Work Experience at the top
\section{Work Experience}

\Job{Senior Key Expert Penetration Tester}
{Siemens Corporation}
{Princeton, NJ, USA}
{Oct 2017}
{Present}
{As a delegate in the USA I continue with my previous responsibilities as a penetration tester. Besides that I lead a research project related to Concolic Execution in cooperation with NYU and EURECOM. As the research lead of the team I designed the offsec research agenda, which focused on OT/ICS security assessment.}

\Job{Penetration Tester}
{Siemens AG}
{Munich, Germany}
{Oct 2013}
{Sept 2017}
{As part of the CERT Security Assessment team, I was responsible to lead and execute various penetration tests. Testing Siemens products gives me the opportunity to work with various exotic systems in healthcare, transportation, energy, building technologies, intelligent cities etc... Apart from that, we regularly test third party systems, which are going to be deployed at Siemens. It is a great place to work with very different technologies, such as web, client-server architecture, embedded devices, mobile technologies etc}

\Job{Penetration Tester}
{OPTIMAbit GmbH}
{Munich, Germany}
{Dec 2011}
{Sept 2013}
{I worked as a external consultant for various companies from multinational insurance, banking and telecommunication companies through government agencies to industry leader technology companies. I executed 32 penetration tests, from that 2 Client-Server applications, 4 network assessment and 26 web application tests. This gave me the opportunity to get to know various networks, systems and application frameworks. I deal with customers on a day to day basis.}

\Job{Senior Quality Assurance Engineer}
{Balabit IT Security}
{Budapest, Hungary}
{Jan 2008}
{Oct 2011}
{My job changed a lot during the years, but the one thing that was always there is the low level black- and white-box testing manually and by writing automated test scripts as well. I worked on all products of the company, which gave me deep understanding of firewalls, logging architectures and high availability appliances mostly in linux environment. I gathered deep knowledge from the PHP web interface through the shell script and C background process to the underlying OS internals. I was also a team leader of 3 testers until the company embraced the SCRUM methodology, which made me a SCRUM master. I also worked in the development of our internal systems especially our automated test system, which was written in Python.
}

\Job{Call Centre Advisor}
{British Telecommunications Plc.}
{Glasgow, UK}
{}
{Jul-Dec 2007}
{I went to Glasgow to improve my English, which I did, thanks to my job in the call centre. It was related to my profession since I was selling telephone and Internet services and helped people to solve there issues with their services. Besides this the more important was that it gave a huge boost to my communication and soft skills.}

\Job{Developer Trainee}
{Telenor Hungary}
{Budaörs, Hungary}
{}
{Spring 2007}
{As a trainee I worked mostly on internal projects at one of the 3 mobile service providers of Hungary. I wrote an address and phone book for the whole company with WEB and WAP interface in \emph{PHP}. I worked with an open source MMSC implementation, which was written in C.}

\Job{Assistance in teaching Project Management}
{Budapest University of Technology and Economics}
{Budapest, Hungary}
{}
{Automn 2006}
{I was responsible for keeping touch with the students, help them with their homeworks and give them feedback on their progress. This work and the professor gave me deep understanding of the waterfall project management and the PMBOK methodology.}
